### 2025-07-18 CV2/papers.tex
add paper, semantic scholar api test

\textbf{\href{https://arxiv.org/abs/2405.18031}{Lower Bounds and Optimal Algorithms for Non-Smooth Convex Decentralized Optimization over Time-Varying Networks}} (Dmitry Kovalev, Ekaterina Borodich, Alexander Gasnikov, Dmitrii Feoktistov). \textit{Advances in Neural Information Processing Systems}, 2024.

@@

\textbf{\href{https://link.springer.com/content/pdf/10.1007/978-3-030-54621-2_860-1.pdf}{Decentralized Convex Optimization over Time-Varying Graphs}} (Alexander Rogozin, Alexander Gasnikov, Aleksander Beznosikov, Dmitry Kovalev). \textit{Encyclopedia of Optimization}, 2023.

@@

\textbf{\href{https://link.springer.com/chapter/10.1007/978-3-030-91059-4_18}{Near-optimal decentralized algorithms for saddle point problems over time-varying networks}} (Aleksandr Beznosikov, Alexander Rogozin, Dmitry Kovalev, Alexander Gasnikov). \textit{Optimization and Applications: 12th International Conference, OPTIMA 2021, Petrovac, Montenegro, September 27–October 1, 2021, Proceedings 12}, 2021.

@@

\textbf{\href{https://link.springer.com/chapter/10.1007/978-3-030-91059-4_19}{Towards accelerated rates for distributed optimization over time-varying networks}} (Alexander Rogozin, Vladislav Lukoshkin, Alexander Gasnikov, Dmitry Kovalev, Egor Shulgin). \textit{Optimization and Applications: 12th International Conference, OPTIMA 2021, Petrovac, Montenegro, September 27–October 1, 2021, Proceedings 12}, 2021.

@@

\textbf{\href{http://crm-en.ics.org.ru/journal/article/2685/}{A hypothesis about the rate of global convergence for optimal methods (Newton’s type) in smooth convex optimization}} (Alexander Gasnikov, Dmitry Kovalev). \textit{Computer research and modeling}, 2018.

@@

>>>>

\textbf{\href{https://proceedings.neurips.cc/paper_files/paper/2024/hash/af10f27d0a48175e486a647c06c7a9c6-Abstract-Conference.html}{Lower Bounds and Optimal Algorithms for Non-Smooth Convex Decentralized Optimization over Time-Varying Networks}} (Dmitry Kovalev, Ekaterina Borodich, Alexander Gasnikov, Dmitrii Feoktistov). \textit{Advances in Neural Information Processing Systems}, 2024.

@@

\textbf{\href{https://link.springer.com/rwe/10.1007/978-3-030-54621-2_860-1}{Decentralized convex optimization over time-varying graphs}} (Alexander Rogozin, Alexander Gasnikov, Aleksander Beznosikov, Dmitry Kovalev). \textit{Encyclopedia of Optimization}, 2023.

@@

\textbf{\href{https://link.springer.com/chapter/10.1007/978-3-030-91059-4_18}{Near-optimal decentralized algorithms for saddle point problems over time-varying networks}} (Aleksandr Beznosikov, Alexander Rogozin, Dmitry Kovalev, Alexander Gasnikov). \textit{International Conference on Optimization and Applications}, 2021.

@@

\textbf{\href{https://link.springer.com/chapter/10.1007/978-3-030-91059-4_19}{Towards accelerated rates for distributed optimization over time-varying networks}} (Alexander Rogozin, Vladislav Lukoshkin, Alexander Gasnikov, Dmitry Kovalev, Egor Shulgin). \textit{International Conference on Optimization and Applications}, 2021.

@@

\textbf{\href{https://crm-en.ics.org.ru/journal/article/references/2685/}{A hypothesis about the rate of global convergence for optimal methods (Newton’s type) in smooth convex optimization}} (Alexander Gasnikov, Dmitry Kovalev). \textit{Computer research and modeling}, 2018.

@@

\textbf{\href{https://arxiv.org/abs/2507.09823}{Nesterov Finds GRAAL: Optimal and Adaptive Gradient Method for Convex Optimization}} (Ekaterina Borodich, Dmitry Kovalev). \textit{arXiv preprint arXiv:2507.09823}, 2025.
